Geometric variational problems

### 2020-11-13 NSF2020/Description/newspecificaim3.tex
yny new sa2 3 prelim

We include a background flow by replacing the third equation in
\eqref{eq:stokes} with the condition $(\mathbf{u} -
\mathbf{u}_{\infty})(\mathbf{x}) \to \mathbf{0}$ as $|\mathbf{x}| \to
\infty$. To incorporate the far-field flow, we use the representation 
\begin{align}
\label{PowerMiranda}
  {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
    \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + 
                 R(\cdot, {\bf a}_i) {\bf G}_i.
\end{align}
where $S$ and $R$ are stokeslets and rotlets supported at the respective
particle centers and $K\boldsymbol{eta}$ is a layer potential for the
unknown density function $\boldsymbol{\eta}.$ The
representation~\eqref{PowerMiranda} automatically satisfies all
equations, with the exception of the rigid motion conditions. The rigid
motion conditions follow by requiring the viscous stress vanishes across
the particle boundaries.

>>>>

We include a background flow by replacing the third equation in
\eqref{eq:stokes} with the condition $(\mathbf{u} -
\mathbf{u}_{\infty})(\mathbf{x}) \to \mathbf{0}$ as $|\mathbf{x}| \to
\infty$. To incorporate the far-field flow, we use the representation 
\begin{align}
\label{PowerMiranda}
  {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
    \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + 
                 R(\cdot, {\bf a}_i) {\bf G}_i.
\end{align}
where $S$ and $R$ are stokeslets and rotlets supported at the respective
particle centers  \cite{leal_2007} and $K\boldsymbol{\eta}$ is a layer potential for the
unknown density function $\boldsymbol{\eta}.$ The
representation~\eqref{PowerMiranda} automatically satisfies all
equations, with the exception of the rigid motion conditions. The rigid
motion conditions follow by requiring the viscous stress vanishes across
the particle boundaries.

### 2020-11-13 NSF2020/Description/preliminarywork.tex
yny new sa2 3 prelim

The PIs BQ, RR, YNY and Peter Fu initiated a collaboration in summer, 2020. 
The present proposal is the outgrowth of this collaboration. We have created
a compact numerical solver and included background flow in the simulations. 
The background flow enters by replacing the third equation in \eqref{eq:stokes} 
with the condition $(\mathbf{u} -\mathbf{u}_{\infty})(\mathbf{x}) 
\to \mathbf{0}$ as $|\mathbf{x}| \to \infty$. To incorporate the far-field flow, 
and using the representation 
\begin{align}
\label{PowerMiranda}
  {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
    \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + 
                 R(\cdot, {\bf a}_i) {\bf G}_i.
\end{align}
The symbols $S$ and $R$ are stokeslets and rotlets supported at the respective
particle centers \cite{leal_2007} and $K\boldsymbol{eta}$ is a layer potential for the
unknown density function $\boldsymbol{\eta}.$ The
representation~\eqref{PowerMiranda} automatically satisfies all
equations, with the exception of the rigid motion conditions. The rigid
motion conditions follow by requiring the viscous stress vanishes across
the particle boundaries.

\begin{wrapfigure}[13]{l}{0.30\textwidth}
\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
  \vspace{-8pt}
\caption{
\label{fig:bierror}  
\footnotesize The false color map shows how numerical quadrature of
  layer potentials loses accuracy near the particle boundaries.  The
  color bar is for $\log_{10}.$}
\end{wrapfigure}
\textbf{Novel reciprocal identities.} 
The force and torque formulas~\eqref{forceandtorque} require the
hydrophobic stress along the particle boundaries. Unfortunately,
standard quadrature formulas to estimate $\nabla u$ on the particle
boundaries introduces large amounts of quadrature error
(Figure~\ref{fig:bierror}). Therefore, it is useful to devise reciprocal
identities for the force and torque on body $i$ that does not
require integration along body $i$. One identity, that we have proved,
is
\begin{align}
    \label{eq:reciprocal}
{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}
[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
\end{align}
for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
equation when only the contribution from particle $i$ is considered and
$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
Because of the double layer potential jump relations, \eqref{eq:reciprocal} 
does not require knowledge of $\nabla u$ on the particle boundary, and this
is enormously beneficial for calculating force and torque.

>>>>

The PIs BQ, RR, YNY and Peter Fu initiated a collaboration in summer, 2020. 
The present proposal is the outgrowth of this collaboration. We have created
a compact numerical solver and included background flow in the simulations. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%For Specific Aim 3
%The background flow enters by replacing the third equation in \eqref{eq:stokes} 
%with the condition $(\mathbf{u} -\mathbf{u}_{\infty})(\mathbf{x}) 
%\to \mathbf{0}$ as $|\mathbf{x}| \to \infty$. To incorporate the far-field flow, 
%and using the representation 
%\begin{align}
%\label{PowerMiranda}
%  {\bf u} = {\bf u}_{\infty} + K\boldsymbol{\eta} + 
%    \sum_{i=1}^N S(\cdot, {\bf a}_i) {\bf F}_i + 
%                 R(\cdot, {\bf a}_i) {\bf G}_i.
%\end{align}
%The symbols $S$ and $R$ are Stokeslets and rotlets supported at the respective
%particle centers \cite{leal_2007} and $K\boldsymbol{eta}$ is a layer potential for the
%unknown density function $\boldsymbol{\eta}.$ The
%representation~\eqref{PowerMiranda} automatically satisfies all
%equations, with the exception of the rigid motion conditions. The rigid
%motion conditions follow by requiring the viscous stress vanishes across
%the particle boundaries.

%\begin{wrapfigure}[13]{l}{0.30\textwidth}
%\centerline{\includegraphics[width=0.30\textwidth]{figures/BIError.pdf}}
%  \vspace{-8pt}
%\caption{
%\label{fig:bierror}  
%\footnotesize The false color map shows how numerical quadrature of
%  layer potentials loses accuracy near the particle boundaries.  The
%  color bar is for $\log_{10}.$}
%\end{wrapfigure}
%\textbf{Novel reciprocal identities.} 
%The force and torque formulas~\eqref{forceandtorque} require the
%hydrophobic stress along the particle boundaries. Unfortunately,
%standard quadrature formulas to estimate $\nabla u$ on the particle
%boundaries introduces large amounts of quadrature error
%(Figure~\ref{fig:bierror}). Therefore, it is useful to devise reciprocal
%identities for the force and torque on body $i$ that does not
%require integration along body $i$. One identity, that we have proved,
%is
%\begin{align}
%    \label{eq:reciprocal}
%{\bf F}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i}
%[\boldsymbol{\sigma}_{ij} + \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S,\quad
%{\bf G}_{\text{hydro},i} = \sum_{j \neq i} \int_{\partial P_i} ({\bf
%  x}-\mathbf{a}_i) \times [\boldsymbol{\sigma}_{ij} +
%  \boldsymbol{\sigma}_{ji}]\boldsymbol{\nu}\,\dif S, 
%\end{align}
%for $i=1,\ldots,N$. Here, $u_i$ is the solution of the screened Laplace
%equation when only the contribution from particle $i$ is considered and
%$\boldsymbol{\sigma}_{ij} = \rho^{-1} u_iu_j {\bf I} + \rho(\nabla u_i
%\cdot \nabla u_j {\bf I} - 2 \nabla u_i \otimes \nabla u_j)$.
%Because of the double layer potential jump relations, \eqref{eq:reciprocal} 
%does not require knowledge of $\nabla u$ on the particle boundary, and this
%is enormously beneficial for calculating force and torque.
